Jean Pockets and Gender

### 2024-04-22 paper/paper.qmd
clean

## read in cleaned data 
cleaned_pocket_area_data = read_csv(
  file = here::here("data/analysis_data/cleaned_pocket_area_data.csv"),
  show_col_types = FALSE
)
```

@@

## JSON Dataset and cleaning

>>>>

## read in cleaned data 
cleaned_area_data = read_csv(
  file = here::here("data/analysis_data/cleaned_area_data.csv"),
  show_col_types = FALSE
)
```

@@

## JSON Dataset and cleaning
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-cleaned_area_data
#| tbl-cap: Sample of Cleaned Pocket Area Data

head (cleaned_area_data, 5) |>
  kable(
    col.names = c("brand","style","men_women","pocket_area","price"),
  booktabs = TRUE
  )
```
